Light inextensible strings (thread) under tension in the Schwarzschild geometry

### 2021-01-26 physics_educator_rebuttal.txt

It now reads "Here I interpret a straight line as the path adopted by
a stationary, light inexensible string under tension passing between
two points"

There is a little bit of repetition in the revised manuscript, but I
think it is worth it for the extra clarity.

> 2. large (but finite) amounts of string are required to... (second
> line after Eq. 3) why large amounts are needed since w is small?

That is an extremely good observation.  The word "large" is
inappropriate and misleading here, I think.  Asymptotic expansions can
be confusing and what I meant to say was that the ratio of proper
string length to Euclidean string length (that is, length as estimated
by the Euclidean formula (1+r)-1 where 'r' is circumferential radius)
approaches infinity.  But the word "large" is not right here, and I
have rephrased accordingly.

I have also realised that this equation and the preceding one for
small w can be made much more comprehensible by giving an example, and
I have included two examples using solar-mass black holes.

### 2021-01-26 string_physics_educator_revision2.tex
fixes #25

(compare the flat space string length of $2Mw$).  This would indicate
 that, close to the Schwarzschild radius $r=2M$, large (but finite)
 amounts of string are required to connect two points with slightly
 differing radial coordinates.  Passing to the case $w\gg 1$ we have
 an asymptotic expansion that begins

% \begin{equation}\label{asymptotic_ell_properunits}
%   \ell = w +  \frac{1}{2}\log w + \frac{1}{2} + \log(2)  +  \frac{1}{8}w^{-1} + O(w^{-2}),
% \end{equation}
% 
\begin{equation}\label{asymptotic_ell}
  \ell = 2M\left(w +  \frac{1}{2}\log w + \frac{1}{2} + \log(2)  +  \frac{1}{8}w^{-1} + O(w^{-2})\right),
\end{equation}

\noindent suggesting that there is ``extra space'', sensible at large
distances from the event horizon, with radial strings being
arbitrarily longer than flat space would allow: a nice illustration of
the failure of Euclidean geometry.

>>>>

(compare the flat space string length of $2Mw$).  This would indicate
 that, close to the Schwarzschild radius $r=2M$, more string is
 required to connect two points with slightly differing radial
 coordinates.  Taking a solar-mass black hole and $w=10^{-3}$ as an
 example, the proper length computed in flat space would be
 $10^{-2}\cdot 2M\simeq 3\,\mathrm{m}$---compare $\sim
 187\,\mathrm{m}$ from equation~\ref{ell}.  Passing to the case $w\gg
 1$ we have an asymptotic expansion that begins

% \begin{equation}\label{asymptotic_ell_properunits}
%   \ell = w +  \frac{1}{2}\log w + \frac{1}{2} + \log(2)  +  \frac{1}{8}w^{-1} + O(w^{-2}),
% \end{equation}
% 
\begin{equation}\label{asymptotic_ell}
  \ell = 2M\left(w +  \frac{1}{2}\log w + \frac{1}{2} + \log(2)  +  \frac{1}{8}w^{-1} + O(w^{-2})\right).
\end{equation}

\noindent The discrepancy between the flat-space result of $2Mw$ and
equation~\ref{asymptotic_ell} suggests that, even far from the event
horizon, radial strings are arbitrarily longer than flat space would
imply: a nice illustration of the failure of Euclidean geometry.
Again taking a solar mass black hole but with $w=2\times 10^7$
(corresponding to the orbital radius of Mercury) the difference
between the classical result and equation~\ref{asymptotic_ell} is
about $28\,\mathrm{km}$ of extra string.  However, the prediction is
unlikely to be the basis of a fourth test of general relativity---the
others being Shapiro time delay, bending of starlight, and the
perihelion advance of Mercury~\cite{einstein1916}---as the Sun is not
inside its own Schwarzschild radius.
